\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-12 analytics.tex
add export

What this means is that Skedge is not seen as an experiment or a proof of concept that is not production-ready. Rather, its traffic patterns show that it is consistenly \emph{relied upon} by students and used for its intended purpose in times of biggest course scheduling need. %, and the same can be seen with other usage measures such as schedule exporting and clicking on the Wikipedia-style embedded links (Figures \ref{fig:exports} and \ref{fig:linksearches}, respectively).

@@

Figure \ref{fig:searchtypes} validates the hypothesis made in Section 2.3 regarding the search interface design, demonstrating that the \emph{department code} and \emph{course number} search modes dominate user searches, accounting for over 85\% of all searches on Skedge. With this knowledge, bringing out the tucked-away, nondistinct field for this search in CDCS into prominence is a usability design choice that accomodates empirical usage.

@@

  Of the total 45,466 searches on Skedge logged since November 2nd 2015, 89.4\% (40,625) of searches produce nonempty search results, whereas 10.6\% (4,841) of searches come up empty. This already is evidence of an effective search mechanism, but of those empty searches, the vast majority

  Can learn from these searches. This is the same method WolframAlpha describes its team using to improve their freeform input system \cite{wolfram2}.

@@

    ``{\tt tuesday 3:25-4:40}'' \newline ``{\tt TR 3:25-4:40}'' \newline ``{\tt m/w}'' \newline ``{\tt classes tuesdays and thursdays between 11:05 and 12:20}'' \newline ``{\tt weekend summer 2016}''
    & \parbox[c]{\hsize}{Better day-of-the-week handling} \\ \hline

@@

    ``{\tt new csc courses}'' 
    & The word ``{\tt courses}'' (somewhat common) \\ \hline

@@

    ``{\tt stt212 vs mth201}'' \newline ``{\tt stt212 OR mth201}'' 
    & Searching multiple queries at the same time \\ \hline

@@

    ``{\tt MTH 2*}'' 
    & Using ``{\tt *}'' instead of an omission (e.g. ``{\tt MTH 2}'' would work) \\ \hline

    \hline
  \end{tabular}
  \caption{Example of search queries that produced no results but that indicate demand for added search features. The corresponding features that currently lack in SkedgeQL are described on the right.}
  \end{figure}

@@

    ``{\tt game of thrones}''
    & ``{\tt fun classes}''
    & ``{\tt fun classes in csc}''
    \\ \hline

@@

    \hline
  \end{tabular}
  \caption{Humerous search submissions}
  \end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1.0\textwidth]{images/graph/exports}

  \caption{Etc}
  \label{fig:exports}
\end{figure}

Success! (broken on cdcs)

>>>>

What this means is that Skedge is not seen as an experiment or a proof of concept that is not production-ready. Rather, its traffic patterns show that it is consistenly \emph{relied upon} by students and used for its intended purpose in times of biggest course scheduling need.

@@

Figure \ref{fig:searchtypes} validates the hypothesis made in Section 2.3 regarding the search interface design, demonstrating that the \emph{department code} and \emph{course number} search modes dominate user searches, accounting for over 85\% of all searches on Skedge. With this knowledge, bringing out the tucked-away, nondistinct field for this search in CDCS into prominence is a usability design choice that accomodates an empirically verified use case.

@@

  Of the total 45,466 searches on Skedge logged since November 2nd 2015, 89.4\% (40,625) of searches produce nonempty search results, whereas 10.6\% (4,841) of searches come up empty.

  This already is evidence of an effective search mechanism, but of those empty searches, the vast majority (92\%) contain typos or are for courses that simply don't exist. The other significant portion of searches include instructor names without the requisite ``taught by'' for SkedgeQL to pick it up as an instructor search, and such a fix could easily be made.

  This type of analysis can powerfully indicate holes in the query language (i.e. searches intuitive for users) that ought to be fixed, which is the same method WolframAlpha describes its team using to improve their freeform input system \cite{wolfram2}. Figure \ref{fig:empty-queries} lists a few notable examples of this nature. (Figure \ref{fig:funny-queries} lists a few funny queries I came across.)

@@

    ``{\tt tuesday 3:25-4:40}'' \newline ``{\tt m/w}'' \newline ``{\tt classes tuesdays and thursdays between 11:05 and 12:20}'' \newline ``{\tt weekend summer 2016}''
    & \parbox[c]{\hsize}{Better day-of-the-week handling} \\ \hline

@@

    ``{\tt new csc courses}'' 
    & The word ``{\tt courses}'' (somewhat common with advanced query types) \\ \hline

    ``{\tt curriculum change}'' 
    & Alternative for ``{\tt new}'' keyword \\ \hline

@@

    ``{\tt stt212 vs mth201}'' \newline ``{\tt stt212 OR mth201}'' \newline ``{\tt csc 2\{4,8\}2}'' \newline ``{\tt csc 242|282}''
    & Searching multiple queries at the same time \\ \hline

@@

    ``{\tt MTH 2*}'' \newline ``{\tt csc 2xx}''
    & Using ``{\tt *}'' instead of an omission (e.g. ``{\tt MTH 2}'' would work) \\ \hline

    \hline
  \end{tabular}
  \caption{Example of search queries that produced no results but that indicate demand for added search features. The corresponding features that currently lack in SkedgeQL are described on the right.}
  \label{fig:empty-queries}
  \end{figure}

@@

    ``{\tt game of thrones}''
    & ``{\tt interesting courses}''
    & ``{\tt fun classes in csc}''
    \\ \hline

@@

    \hline
  \end{tabular}
  \caption{Humorous search submissions}
  \label{fig:funny-queries}
  \end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{images/graph/exports}

  \caption{Different types of schedule exporting over time}
  \label{fig:exports}
\end{figure}

In Section 2.2.5 (on the design of Skedge's schedule exporting), a major usability improvement claimed was the ability to export schedules to the {\tt .ics} format, a widely used format for many calendar applications, as well as offering functional Google Calendar export. Figure \ref{fig:exports} shows usage of the export functions over time, demonstrating its consistent and healthy use (traffic surges once again in line with major scheduling events.) This data confirms that there is strong demand for exporting to {\tt .ics}---it is even more common than Google Calendar export.

### 2016-04-12 design/usability.tex
add export

>>>>

\subsection{Schedule export}

Better CDCS provides two ways for users to export their schedule---as image or to Google calendar--except that the Google Calendar export feature is completely non-functional, telling users that ``{\tt This export tool will only work properly for the Spring of 2015}'' only \emph{after} they authorized the tool to access their Google account.

Notably missing as an export option is the \emph{iCalendar} file format (extension {\tt .ics}), which can be imported into many calendar software products. It is the only format the Mac OS and iOS Calendar applications can accept, to offer one example of very popular products that are therefore unsupported by Better CDCS.

Skedge provides the option for users to export their own or another user's schedule directly to \emph{Google Calendar} (even allowing users to choose a calendar---or create a new one for Skedge---to insert their courses into), as an \emph{image} (JPEG, PNG, or SVG), or in {\tt .ics} format (see Figure \ref{fig:sk-export}). The {\tt .ics} and Google Calendar exports include course codes, titles, locations, and properly repeat courses until the end of the current semester.

\vspace{20pt}

\begin{figure}[ht]
  \centering
  \vspace{2pt}
  \includegraphics[width=14cm]{images/skedge/export}
  \caption{Exporting to Google Calendar (note the other export options on the top right)} \label{fig:sk-export}
\end{figure}

\clearpage
